### 2014-07-30 paper/paper.tex
Extended the results table. Added the beginnings of a results table. About to get meg to look at what I have so far

%TODO note that my solution is unconstrained

@@

@@

@@

Table \ref{table:comparison} shows the performance of the classifier produced
for this project ranks compared to results of the workshop participants. The
full table (with out this project's results) can be found in table 9 of Nakov
et al. \cite{Nakov2013}.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Run & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        \hline
        Majority Baseline & 29.19 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers by F-score.}
    \label{table:comparison}
\end{table}

%TODO finsh table

>>>>

@@

TODO establish baseline here

@@

Since the \textit{test set} is random subset of the corpus, the results of the
classifier can vary slightly between runs. In order to effectively evaluate the
performance of the classifier under certain conditions each experiment is
conducted 3 times and averaged.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c|c|r|r|r|r|}
        \hline
        Description & Stopwords & Run 1 & Run 2 & Run 3 & $\mu$ F\\
        \hline
        MaxEnt      & Yes       & 0.0   & 0.0   & 0     & 0 \\
        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
        Naive Bayes & Yes       & 0.0   & 0.0   & 0     & 0 \\
        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Results of variations on feature selection and training. Sorted by
        average F-score.}
    \label{table:results}
\end{table}

@@

Table \ref{table:comparison} shows the performance of the classifier produced
for this project compared to results of the workshop participants. The full
table (with out this project's results) can be found in table 9 of Nakov et al.
\cite{Nakov2013}.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Team & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        AMI\&ERIC  & 62.55 \\
        FBM        & 61.17 \\
        AVAYA      & 60.84 \\
        SAIL       & 60.14 \\
        UT-DB      & 59.87 \\
        FBK-irst   & 59.76 \\
        nlp.cs.aueb.gr & 58.91 \\
        UNITOR     & 58.27 \\
        LVIC-LIMSI & 57.14 \\
        Unigon     & 56.96 \\
        NILC\_USP   & 56.31 \\
        DataMining & 55.52 \\
        ECNUCS     & 55.05 \\
        nlp.cs.aueb.gr & 54.73 \\
        ASVUniOfLeipzig & 54.56 \\
        SZTE-NLP   & 54.33 \\
        CodeX      & 53.89 \\
        Oasis      & 53.84 \\
        \textbf{Best MaxEnt}& \textbf{53.32} \\
        NTNU       & 53.23 \\
        UoM        & 51.81 \\
        SSA-UO     & 50.17 \\
        SenselyticTeam & 50.10 \\
        $\ldots$ & $\ldots$ \\
        9 more teams &  \textless\ 50 \\
        $\ldots$ & $\ldots$ \\
        \hline
        Majority Baseline & 29.19 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
        workshop. Sorted by F-score.}
    \label{table:comparison}
\end{table}
